Supplementary Content

### 2022-02-03 experiments/1_figures_main_ms/Understand_PB.Rmd
large number of updates, no changes in results though

## Figure 5
Region of bistability by diversity and number of strains.

![alt text](figure_5_v2_allstrains.png)

@@

```{r fig3_prep}
ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data_1e6.RDS"))

>>>>

## Figure 5

Region of bistability by diversity and number of strains.

(*Graphs should be remade/reinserted.*)

@@

```{r fig3_prep}
ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))

### 2022-02-03 experiments/2_supplement/supplement.Rmd
large number of updates, no changes in results though

```{r repl_meth1, echo=FALSE, eval = FALSE}
repl_meth <- readRDS(here("experiments/0_ss_finding/replication_method/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
temp_meth <- readRDS(here("experiments/0_ss_finding/temporal_method/data/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
## To be completed.
plot_ss_result1(repl_meth,
                result_index = 1,
                filename_prefix = NULL,
                save_image_file = FALSE)
```

@@

```{r temp_meth1, echo=FALSE, eval = FALSE}
plot_ss_result3(temp_meth, 1)
```

@@

```{r both_meth1, echo=FALSE, eval = FALSE}
repl_method_1 <- repl_meth$ss_res[[1]] %>%
     mutate(time = NA,
            direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  select(names(temp_meth$ssfind_result[[1]]))

@@

```{r echo = FALSE, eval = FALSE}
stab_data <- readRDS(here("experiments/0_ss_finding/replication_method/9_strains/data/small_stab_data_1e6_x2x6_factorial.RDS"))

@@

```{r echo = FALSE, eval = FALSE}
all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "SR") %>%
  ggplot(aes(x = var_gmax)) +
  #ggplot(aes(x = var_gmax,
  #           col = as.factor(num_strains))) +
  geom_line(aes(y = hyst_min_log), lwd = 2, alpha = 0.8) +
  geom_line(aes(y = hyst_max_log), lwd = 2, alpha = 0.8) +
  facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  #guides(col = guide_legend(title="Number of strains")) +
  theme(
    legend.position="top"
    #strip.background = element_blank(),
    #strip.text.x = element_blank()
  ) +
  geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3)

@@

```{r wait_time_1e6, eval = FALSE}
wait_time <- "1e+06"

#stab_2s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
#stab_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
#stab_6s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))
stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

#all_stab <- stab_2s %>%
  #bind_rows(stab_2s_sub1) %>%
#  bind_rows(stab_3s) %>%
  #bind_rows(stab_3s_sub1) %>%
#  bind_rows(stab_6s) %>%
  #bind_rows(stab_6s_sub1) %>%
#  bind_rows(stab_9s)
  #bind_rows(stab_9s_sub1) %>%
  #bind_rows(stab_9s_diff3)

all_stab <- stab_9s
```

```{r wait_time_1e6_2, eval = FALSE}
p1 <- fig_div_vs_o2diff_1strain_7row(all_stab,
                                     which_strain = 9,
                                     figure_title = "1e6 wait time, 9 strains")
#p1
p2 <- fig_resilience_vs_div(all_stab, which_strain = 9, figure_title = " ") 
#p2
p1 + p2

@@

@@

```{r wait_time_1e5, eval = FALSE}

wait_time <- "1e+05"

stab_2s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
stab_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
stab_6s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))
stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

all_stab <- stab_2s %>%
  #bind_rows(stab_2s_sub1) %>%
  bind_rows(stab_3s) %>%
  #bind_rows(stab_3s_sub1) %>%
  bind_rows(stab_6s) %>%
  #bind_rows(stab_6s_sub1) %>%
  bind_rows(stab_9s)
  #bind_rows(stab_9s_sub1) %>%
  #bind_rows(stab_9s_diff3)

fig_div_vs_o2diff_multistrain(all_stab = all_stab,
                  which_strains = c(2, 3, 6, 9),
                  figure_title = paste0("Wait time = ", wait_time))

@@

```{r eval = FALSE}
wait_time <- "1e+04"
ss_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/ss_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))

@@

```{r eval = FALSE}
fig_state_vs_o2diff(only_SB_variable[13,])
```

@@

```{r eval = FALSE}
fig_state_vs_o2diff(only_SB_variable[14,])
```

@@

### Even shorter wait times

```{r wait_time_1e4, eval = FALSE}

wait_time <- "1e+04"

stab_2s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
stab_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
stab_6s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))
stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

all_stab <- stab_2s %>%
  #bind_rows(stab_2s_sub1) %>%
  bind_rows(stab_3s) %>%
  #bind_rows(stab_3s_sub1) %>%
  bind_rows(stab_6s) %>%
  #bind_rows(stab_6s_sub1) %>%
  bind_rows(stab_9s)
  #bind_rows(stab_9s_sub1) %>%
  #bind_rows(stab_9s_diff3)

fig_div_vs_o2diff_multistrain(all_stab = all_stab,
                  which_strains = c(2, 3, 6, 9),
                  figure_title = paste0("Wait time = ", wait_time))

```{r wait_time_1e3, eval = FALSE}

wait_time <- "1e+03"

stab_2s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
stab_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
stab_6s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))
stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

all_stab <- stab_2s %>%
  #bind_rows(stab_2s_sub1) %>%
  bind_rows(stab_3s) %>%
  #bind_rows(stab_3s_sub1) %>%
  bind_rows(stab_6s) %>%
  #bind_rows(stab_6s_sub1) %>%
  bind_rows(stab_9s)
  #bind_rows(stab_9s_sub1) %>%
  #bind_rows(stab_9s_diff3)

fig_div_vs_o2diff_multistrain(all_stab = all_stab,
                  which_strains = c(2, 3, 6, 9),
                  figure_title = paste0("Wait time = ", wait_time))

```{r wait_time_1e2, eval = FALSE}

wait_time <- "1e+02"

stab_2s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
stab_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
stab_6s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))
stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

all_stab <- stab_2s %>%
  #bind_rows(stab_2s_sub1) %>%
  bind_rows(stab_3s) %>%
  #bind_rows(stab_3s_sub1) %>%
  bind_rows(stab_6s) %>%
  #bind_rows(stab_6s_sub1) %>%
  bind_rows(stab_9s)
  #bind_rows(stab_9s_sub1) %>%
  #bind_rows(stab_9s_diff3)

fig_div_vs_o2diff_multistrain(all_stab = all_stab,
                  which_strains = c(2, 3, 6, 9),
                  figure_title = paste0("Wait time = ", wait_time))

@@

```{r echo = FALSE, fig.height=10, eval = FALSE}

>>>>

```{r repl_meth1, echo=FALSE, eval = TRUE}
repl_meth <- readRDS(here("experiments/0_ss_finding/replication_method/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
temp_meth <- readRDS(here("experiments/0_ss_finding/temporal_method/data/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
## To be completed.
plot_ss_result1(repl_meth,
                result_index = 1,
                filename_prefix = NULL,
                save_image_file = FALSE)
```

@@

```{r temp_meth1, echo=FALSE, eval = TRUE}
plot_ss_result3(temp_meth, 1)
```

@@

```{r both_meth1, echo=FALSE, eval = TRUE}
repl_method_1 <- repl_meth$ss_res[[1]] %>%
     mutate(time = NA,
            direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  select(names(temp_meth$ssfind_result[[1]]))

@@

```{r echo = FALSE, eval = TRUE}
stab_data <- readRDS(here("experiments/0_ss_finding/replication_method/9_strains/data/small_stab_data_1e6_x2x6_factorial.RDS"))

@@

```{r echo = FALSE, eval = TRUE}
all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "SR") %>%
  ggplot(aes(x = var_gmax)) +
  #ggplot(aes(x = var_gmax,
  #           col = as.factor(num_strains))) +
  geom_line(aes(y = hyst_min_log), lwd = 2, alpha = 0.8) +
  geom_line(aes(y = hyst_max_log), lwd = 2, alpha = 0.8) +
  facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  #guides(col = guide_legend(title="Number of strains")) +
  theme(
    legend.position="top"
    #strip.background = element_blank(),
    #strip.text.x = element_blank()
  ) +
  geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3)

@@

```{r wait_time_1e6, eval = TRUE}
all_stab <- readRDS(here("experiments/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))

wait_time <- 1e6
num_strains <- 9
plot_here <- all_stab %>%
  filter(waittime == wait_time)
p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(wait_time,
                                                           " wait time,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ") 
p1 + p2

@@

```{r wait_time_1e5, eval = TRUE}

wait_time <- 1e5
num_strains <- 9
plot_here <- all_stab %>%
  filter(waittime == wait_time)
p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(wait_time,
                                                           " wait time,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ") 
p1 + p2
```

```{r wait_time_1e4, eval = TRUE}

wait_time <- 1e4
num_strains <- 9
plot_here <- all_stab %>%
  filter(waittime == wait_time)
p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(wait_time,
                                                           " wait time,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ") 
p1 + p2
```

```{r wait_time_1e3, eval = TRUE}

wait_time <- 1e3
num_strains <- 9
plot_here <- all_stab %>%
  filter(waittime == wait_time)
p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(wait_time,
                                                           " wait time,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ") 
p1 + p2
```

```{r wait_time_1e2, eval = TRUE}

wait_time <- 1e2
num_strains <- 9
plot_here <- all_stab %>%
  filter(waittime == wait_time)
p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(wait_time,
                                                           " wait time,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ") 
p1 + p2
```

@@

@@

```{r eval = TRUE}
wait_time <- "1e+04"
ss_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/ss_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))

@@

```{r eval = TRUE}
fig_state_vs_o2diff(only_SB_variable[13,])
```

@@

```{r eval = TRUE}
fig_state_vs_o2diff(only_SB_variable[14,])
```

@@

@@

```{r echo = FALSE, fig.height=10, eval = TRUE}
